The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-10 src/rev1_reply_comments.tex
Tiny updates.

              Finally, the very good fit of our model to official infection rates across
              age groups increases our confidence that we manage to match actual meeting
              patterns. If we were far off for, for example, the number of work contacts,
              we would not be able to match either the infections of individuals in the
              working age (35-59) or of those that mostly do not work anymore (60-79).
          }
    \item They state that susceptibility is dependent on age. This requires references
          and needs to be further explained. Also, younger populations are highly susceptible,
          they may just not contribute transmission as much. On that same note, infectiousness
          may not be independent of age

@@

              We base our assumption on infectiousness being independent of age on
              \citep{Jones2021}. That paper reports only slight differences in viral
              loads between German adults and children: ``The least infectious youngest
              children have 78\% (61, 94) of the peak culture probability of adults aged
              45 to 55''. Furthermore, they caution that these lower numbers may be due
              to different sample taking---such as the usage of smaller pediatric swab
              devices---rather than actual lower viral loads and conclude that the
              differences, if existent, are likely not clinically relevant.

                  {\bf ToDo: Check paper suggestion
                      \url{https://doi.org/10.1093/infdis/jiaa691} -- are they actually checking
                      infectiousness conditional on contact type? Or could we even reproduce
                      what they are doing (not suggesting we should, certainly no need to spend
                      time on it)}
              %   In any case, while the jury is certainly still out on that particular issue, we are confident that different assumptions would not change our results much. 
          }
    \item It is not accurate that the vaccines stop transmission. This has to be adapted
          accordingly. Also, the authors should state which vaccines they based this
          analysis on, as in which ones were in use in Germany at that time and how does
          that affect the relative transmissibility as it cannot be assumed that all
          vaccines will have the same effect.

>>>>

              Finally, the very good fit of our model to official infection rates across
              age groups increases our confidence that we manage to match actual meeting
              patterns. If we were far off for, for example, the number of work
              contacts, we would not be able to match either the infections of
              individuals during working age (35-59) or of those that mostly do not work
              anymore (60-79). 
            }
    \item They state that susceptibility is dependent on age. This requires references
          and needs to be further explained. Also, younger populations are highly susceptible,
          they may just not contribute transmission as much. On that same note, infectiousness
          may not be independent of age

@@

              We base our assumption on infectiousness being independent of age on
              \citet{Jones2021}. That paper reports only slight differences in viral
              loads between German adults and children: ``The least infectious youngest
              children have 78\% (61, 94) of the peak culture probability of adults aged
              45 to 55''. Furthermore, they caution that these lower numbers may be due
              to different sample taking---such as the usage of smaller pediatric swab
              devices---rather than actual lower viral loads and conclude that the
              differences, if existent, are likely not clinically relevant.

                  {\bf \color{red} ToDo: Check paper suggestion
                      \url{https://doi.org/10.1093/infdis/jiaa691} -- are they actually checking
                      infectiousness conditional on contact type? Or could we even reproduce
                      what they are doing (not suggesting we should, certainly no need to spend
                      time on it)}

              In any case, while the jury is certainly still out on that particular
              issue, we are confident that different assumptions would not be quantitatively
              meaningful to change our results in a significant way.

          }
    \item It is not accurate that the vaccines stop transmission. This has to be adapted
          accordingly. Also, the authors should state which vaccines they based this
          analysis on, as in which ones were in use in Germany at that time and how does
          that affect the relative transmissibility as it cannot be assumed that all
          vaccines will have the same effect.
